### 2019-01-09 paper/sex_selection_spacing-ver2.tex
Add graphs for second births

\begin{figure}[htp]%
\centering
\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
\caption{Sex ratio of ``first'' births by duration of marriage}
\label{fig:sexRatioMarriage}
\end{figure}

@@

\begin{figure}
\centering
\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1}}
\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2}} \\
\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3}} 
\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4}} 
\caption{Ratio of Boys for ``First'' Births by Survey Round}
\label{fig:sex_ratio_recall_rounds}
\end{figure}

>>>>

\begin{figure}[htp]%
\centering
\includegraphics[width=0.9\textwidth]{recall_sex_ratio_marriage}
\caption{Sex ratio of ``first'' births by duration of marriage}
\label{fig:sexRatioMarriage}
\end{figure}

@@

\begin{figure}
\centering
\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1}}
\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2}} \\
\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3}} 
\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4}} 
\caption{Ratio of Boys for ``First'' Births by Survey Round}
\label{fig:sex_ratio_recall_rounds_bo1}
\end{figure}

\begin{figure}
\centering
\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1_bo2}}
\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2_bo2}} \\
\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3_bo2}} 
\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4_bo2}} 
\caption{Ratio of Boys for ``Second'' Births by Survey Round}
\label{fig:sex_ratio_recall_rounds_bo2}
\end{figure}
